### 2017-05-22 sheets/basis-2/sheet-basis-2.tex
Fix solution for exercise 2.12

@@

\begin{answer}
  We define a functor $F : \Set_* \to 1/\Set$ by
  \begin{align*}
    F((A, a)) &\coloneqq (x \mapsto a) \\
    F(h) &\coloneqq h
  \end{align*}
  for all pointed sets $(A, a)$ and $(B, b)$ and functions $h : A \to B$ with $f(a) = b$.
  The second line is valid because
  \[ \begin{split}
    h \circ F((A, a))
    &= (x \mapsto h(a)) \\
    &= (x \mapsto b) \\
    &= F((B, b)).
  \end{split} \]
  Now we define the inverse functor $G : 1/\Set \to \Set_*$ by
  \begin{align*}
    G(f) &\coloneqq (A, f(\star)) \\
    G(h) &\coloneqq h
  \end{align*}
  for all functions $f : 1 \to A$, $g : 1 \to B$ and $h : A \to B$ with $h \circ f = g$.
  The second line is valid because
  \[ \begin{split}
    h(f(\star))
    &= (h \circ f)(\star) \\
    &= g(\star).
  \end{split} \]
  Both functors are mutually inverse on objects because
  \[ \begin{split}
    F(G(f))
    &= F((A, f(\star))) \\
    &= (x \mapsto f(\star)) \\
    &= f
  \end{split} \]
  and
  \[ \begin{split}
    G(F((A, a)))
    &= G(x \mapsto a) \\
    &= (A, a).
  \end{split} \]
  On arrows they are trivially inverse.
\end{answer}

>>>>

\newcommand{\const}[1]{\mathsf{const}_{#1}}

@@

\begin{answer}
  We define a functor $F : \Set_* \to 1/\Set$ by
  \begin{align*}
    F((A, a)) &\coloneqq \const{a} \\
    F(h) &\coloneqq h
  \end{align*}
  for all pointed sets $(A, a)$ and $(B, b)$ and functions $h : A \to B$ with $h(a) = b$.
  Here $\const{x}$ stands for the constant function with value $x$.
  The second line is valid because
  \[ \begin{split}
    h \circ F((A, a))
    &= \const{h(a)} \\
    &= \const{b} \\
    &= F((B, b))
  \end{split} \]
  holds for $h$ as above.
  Now we define the inverse functor $G : 1/\Set \to \Set_*$ by
  \begin{align*}
    G(f) &\coloneqq (A, f(\star)) \\
    G(h) &\coloneqq h
  \end{align*}
  for all functions $f : 1 \to A$, $g : 1 \to B$ and $h : A \to B$ with $h \circ f = g$.
  The second line is valid because
  \[ \begin{split}
    h(f(\star))
    &= (h \circ f)(\star) \\
    &= g(\star).
  \end{split} \]
  Both functors are mutually inverse on objects because
  \[ \begin{split}
    F(G(f))
    &= F((A, f(\star))) \\
    &= \const{f(\star)} \\
    &= f
  \end{split} \]
  and
  \[ \begin{split}
    G(F((A, a)))
    &= G(\const{a}) \\
    &= (A, a).
  \end{split} \]
  On arrows they are trivially inverse.
\end{answer}
